PyQBench: a Python library for benchmarking gate-based quantum computers

### 2023-07-10 txt/manuscript_short.tex

\usepackage{amssymb}

\usepackage{amsthm}
\usepackage{mathtools}

\usepackage{lineno}
\usepackage{listings}

\usepackage{float}

\usepackage{todonotes}
\usepackage{url}

\usepackage{xcolor}

\usepackage{caption}
\usepackage{subcaption}

@@

%
%\lstdefinestyle{mystyle}{
%	backgroundcolor=\color{backcolour},
%	commentstyle=\color{codegreen},
%	keywordstyle=\color{magenta},
%	numberstyle=\tiny\color{codegray},
%	stringstyle=\color{codepurple},
%	basicstyle=\ttfamily\footnotesize,
%	breakatwhitespace=false,
%	breaklines=true,
%	captionpos=b,
%	keepspaces=true,
%	numbers=left,
%	numbersep=5pt,
%	showspaces=false,
%	showstringspaces=false,
%	showtabs=false,
%	tabsize=2
%}
%
%\lstset{style=mystyle}
\lstset{frame=tb,
	language=Python,
	aboveskip=3mm,
	belowskip=3mm,
	showstringspaces=false,
	columns=flexible,
	basicstyle={\small\ttfamily},
%	numberstyle=\color{blue},
%	keywordstyle=\color{blue},
%	commentstyle=\color{PineGreen},
%	stringstyle=\color{ForestGreen},
	breaklines=true,
	breakatwhitespace=true,
	tabsize=3,
	escapeinside={@}{@},
%	literate=
%	{0}{{{\color{red}0}}}1
%	{1}{{{\color{red}1}}}1
%	{2}{{{\color{red}2}}}1
%	{3}{{{\color{red}3}}}1
%	{4}{{{\color{red}4}}}1
%	{5}{{{\color{red}5}}}1
%	{6}{{{\color{red}6}}}1
%	{7}{{{\color{red}7}}}1
%	{8}{{{\color{red}8}}}1
%	{9}{{{\color{red}9}}}1
%    {v0}{{{\color{black}v0}}}1 %% we can not style only numeric literals
%    {v1}{{{\color{black}v1}}}1
}
\restylefloat{table}

@@

\usepackage{amsmath}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{remark}{Remark}
\newtheorem{lemma}{Lemma}
\theoremstyle{definition}
\newtheorem{scheme}{Scheme}

@@

For the synchronous experiment, the part of the output looks similar to the one below. The whole YAML
file can be seen in Section \ref{app:example.} in the supplemental material.
%Consider the particular experiment data
\begin{lstlisting}[language=Python]
data:
- target: 0
  ancilla: 1
  phi: 0.0
  results_per_circuit:
  - name: id
  histogram: {'00': 28, '01': 26, '10': 21, '11': 25}
  mitigation_info:
	target: {prob_meas0_prep1: 0.052200000000000024, prob_meas1_prep0: 0.0172}
	ancilla: {prob_meas0_prep1: 0.05900000000000005, prob_meas1_prep0: 0.0202}
  mitigated_histogram: {'00': 0.2637212373658018, '01': 0.25865061319892463, '10': 0.2067279352110304, '11': 0.2709002142242433}
\end{lstlisting}

>>>>

\usepackage{amsmath,amssymb,amsthm}
\usepackage{caption}
\usepackage{float}
\usepackage{lineno}
\usepackage{listings}
\usepackage{mathtools}
\usepackage{subcaption}
\usepackage{todonotes}
\usepackage{url}
\usepackage{xcolor}

@@

\lstset{frame=tb,
	language=Python,
	aboveskip=3mm,
	belowskip=3mm,
	showstringspaces=false,
	columns=flexible,
	basicstyle={\small\ttfamily},
	breaklines=true,
	breakatwhitespace=true,
	tabsize=3,
	escapeinside={@}{@},
}
\restylefloat{table}

@@

\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{remark}{Remark}
\newtheorem{lemma}{Lemma}
\theoremstyle{definition}
\newtheorem{scheme}{Scheme}

@@

For the synchronous experiment, the part of the output looks similar to the one below. The whole YAML
file can be seen in Section \ref{app:example} in the supplemental material.
%Consider the particular experiment data
\begin{lstlisting}[language=Python]
data:
- target: 0
  ancilla: 1
  phi: 0.0
  results_per_circuit:
  - name: id
  histogram: {'00': 28, '01': 26, '10': 21, '11': 25}
  mitigation_info:
	target: {prob_meas0_prep1: 0.052200000000000024, prob_meas1_prep0: 0.0172}
	ancilla: {prob_meas0_prep1: 0.05900000000000005, prob_meas1_prep0: 0.0202}
  mitigated_histogram: {'00': 0.2637212373658018, '01': 0.25865061319892463, '10': 0.2067279352110304, '11': 0.2709002142242433}
\end{lstlisting}
